aodc

### 2024-02-07 writing/paper_aodc.qmd
Added a median-improvement map for AODC.
Added another map for AODC.

>>>>

## Mapping a typical day

@fig-map-median-improve shows a tile on `r tar_read(median.improve.map.data)$date`.

```{r pred.map.median.improve}
#| label: fig-map-median-improve
#| fig-cap: foofy
IG(tar_read(pred.map.median.improve.path))
```

### Mapping a documented high-AOD event

```{r pred.map.special.time}
#| label: fig-map-special-time
#| fig-cap: foofy2
IG(tar_read(pred.map.special.time.path))
```
